agdarsec -- Total Parser Combinators

### 2017-10-17 doc/paper/main.tex
[ doc ] some changes I had forgotten to push

@@

@@

@@

>>>>

\DeclareUnicodeCharacter{8759}{:\,:}

@@

This can be made formal with the \AR{Success} record type: a \AF{Success}
of type \AB{A} and size {n} is a value of type \AB{A} together with the
leftovers of the input string of size strictly smaller than \AB{n}.

@@

\remark{Implicit Field} Just like the arguments to a function can be
implicit, so can a record's fields. The user can them leave them out
when building a value and they will be filled in by unification.

Coming back to Fritz Ruehr's rhyme, we can define our own \AR{Parser}
type: a parser for things up to size \AB{n} is a function from strings
of length \AB{m} less than \AB{n} to lists of \AR{Success}es of size \AB{m}.

@@

\agrab{Text/Parser/Combinators}{anyChar}

\agrab{Text/Parser/Combinators}{guardM}
